---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# victor

<!-- badges: start -->
<!-- badges: end -->

The goal of victor is to interact with the [Mapbox Vector Tile API](https://docs.mapbox.com/help/glossary/vector-tiles-api/) ( [also here](https://docs.mapbox.com/api/maps/#vector-tiles) ) in R.
Grab a vector tile,  work with it using the simple features package sf.
Plot static maps with ggplot2, tmap, etc.

A [Mapbox Access Token](link here) is required to access the API.
See these instructions ... link to mapdeck instructions?

Inspired and fuelled by:

 - mapdeck
 - protolite
 - ceramic
 - slippymath
 - rmapzen
 - sf
 


## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("adam-gruer/victor")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(victor)
## basic example code
```

